\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Porush Yadav} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1 4374991364} 
\address{
\href{mailto:porushyadav.264@gmail.com}{porushyadav.264@gmail.com} \\ \href{https://www.linkedin.com/in/porush-yadav}{linkedin.com/in/porush-yadav} \\
\href{https://porush.me}{porush.me}
}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
% ---------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{A highly motivated and a versatile architecture student currently doing a 2 year diploma, interested in a part-time job where I can utilize my communicative and team working capabilities in order to work creatively.}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Diploma in Architectural Technician} \hfill {2023 - 2024}\\
Centennial College

{\bf CBSE SSC Grade 12}  \hfill {2010 - 2022}\\
St. Xavier's School

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Python, MySQL, Excel, Git, GitHub, AutoCAD
\\
Soft Skills & Drawing, Cooking, Acting, Organisational skills, Leadership Skills, Interactive skills\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{School Responsibilities} \\
St. Xavier's School \hfill \textit{Delhi, India}
\begin{itemize}
\itemsep -3pt {}
\item Served as a school prefect, gaining valuable experience in leadership and responsibility.
\item Participated in the School Play Fest, contributing a secondary script to improve writing skills.
\item Submitted drawings in various styles, including portraits and landscapes, for inter-school competitions.

\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\item \textbf{Calculus and Graphing}: {Developed a platform to make calculus accessible to individuals with limited prior knowledge. The project aimed to efficiently perform various calculus functions such as limits, differentiation, integration, and graphing through a digital medium.}

\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular} 
\begin{itemize}

\item Write regular blog posts on literature and share sketches on my \href{https://porush.me}{blog}.
\item Enjoy reading fiction novels.
\item Skilled in creating sketches in various styles, including architecture and portraits.
\item Passionate about cooking and experimenting with dishes from different cuisines.

\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
